---
title: "Comparing 6 implicit measures' suitability for individual use"
author: "Ian Hussey & Jamie Cummins"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

# TODO

- add demographics? or rely on Bar-Anan and Nosek's descriptions?

```{r, include=FALSE}
knitr::opts_chunk$set(message=FALSE,
                      warning=FALSE,
                      cache.lazy=FALSE)
```

```{r}

# dependencies
library(tidyverse)
library(knitr)
library(kableExtra)
library(boot)
library(parallel)
library(bayestestR)
library(patchwork)
library(mdthemes)
library(lme4)
library(sjPlot)
library(marginaleffects)
library(emmeans)
library(ggstance)
library(janitor)
# library(merTools) called via merTools:: to avoid namespace collisions between MASS and dplyr

# create necessary directories
dir.create("../../data/results")
dir.create("plots")

# set seed for reproducibility
set.seed(42)

# options
options(knitr.table.format = "html") # necessary configuration of tables

# disable scientific notation
options(scipen = 999)


# function to round all numeric vars in a data frame
round_df <- function(df, n_digits = 3) {
  require(janitor)
  df %>% mutate_if(is.numeric, janitor::round_half_up, digits = n_digits)
}

```

# Load scored data

```{r}

# testing dataset A scored
data_processed_A <- read_rds("../../data/processed/data_processed_testing.rds")

data_processed_iat_D <- read_rds("../../data/processed/data_processed_iat_D.rds") |>
  mutate(domain = as.factor(str_to_sentence(domain)),
         measure = case_when(measure == "iat"  ~ "IAT",
                             measure == "biat" ~ "Brief IAT",
                             measure == "siat" ~ "SC-IAT",
                             measure == "amp"  ~ "AMP",
                             measure == "gnat" ~ "GNAT",
                             measure == "ept"  ~ "EPT"),
         measure = fct_relevel(measure, "IAT", "Brief IAT", "SC-IAT", "AMP", "GNAT", "EPT"))

# retain only session_ids used in the A scored testing dataset
data_processed <- data_processed_iat_D |>
  semi_join(data_processed_A, by = c("session_id", "domain", "measure")) 

```

# RQ1. Proportion of indiviudal scores that are detectably different from zero

## Caterpillar plot

```{r fig.height=4.5, fig.width=6}

p_cis_by_domain <-
  data_processed %>%
  arrange(estimate) %>%
  group_by(domain, measure) %>%
  mutate(ordered_id = row_number()/n()) %>%
  ungroup() %>%
  ggplot() +
  geom_linerange(aes(x = ordered_id, ymin = ci_lower, ymax = ci_upper, color = sig),
                 alpha = 1) +
  geom_point(aes(ordered_id, estimate), size = 0.5, shape = "square") +
  geom_hline(yintercept = 0, linetype = "dotted") +
  mdthemes::md_theme_linedraw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "top") +
  scale_color_viridis_d(end = 0.6, direction = -1) +
  xlab("Ranked participant") +
  ylab("D score") +
  labs(color = "95% CI excludes zero point") +
  facet_grid(measure ~ domain)

p_cis_by_domain

```

# Predictions

```{r}

dat <- data_processed |>
  mutate(abs_estimate = abs(estimate)) |>
  dplyr::select(measure, domain, abs_estimate, ci_width)
  # group_by(domain, measure) |>
  # summarize()

ggplot(dat, aes(abs_estimate, ci_width)) +
  geom_point(alpha = 0.25) +
  facet_grid(measure ~ domain) +
  geom_smooth(method = "lm", fullrange = TRUE)

fit <- lmer(ci_width ~ abs_estimate * measure + (1 | domain),
            data = dat)

plot_model(fit, type = "int")

# From inquisit race IAT script:
# values.magnitude = "little to no";
# 	if( abs(expressions.d) > 0.15 ) values.magnitude = "a slight";
# 	if( abs(expressions.d) > 0.35 ) values.magnitude = "a moderate";
# 	if( abs(expressions.d) >= 0.65 ) values.magnitude = "a strong";
	
dat_for_pred <- 
  bind_rows(
    mutate(distinct(dat, measure, domain), abs_estimate = 0.00),
    mutate(distinct(dat, measure, domain), abs_estimate = 0.15),
    mutate(distinct(dat, measure, domain), abs_estimate = 0.35),
    mutate(distinct(dat, measure, domain), abs_estimate = 0.65),
  ) |>
  filter(domain == "Race")
  
dat_pred <- dat_for_pred |>
  mutate(ci_width_predicted = predict(fit, newdata = dat_for_pred),
         ci_lower_predicted = abs_estimate - ci_width_predicted/2,
         ci_upper_predicted = abs_estimate + ci_width_predicted/2) |>
  arrange(measure, abs_estimate) |>
  mutate_if(is.numeric, round_half_up, digits = 2) |>
  mutate(result = paste0(ci_lower_predicted, ", ", ci_upper_predicted))

dat_pred |>
  dplyr::select(measure, domain, abs_estimate, result) |>
  kable() |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# ggplot(dat_pred, aes(as.factor(abs_estimate), abs_estimate, color = measure)) +
#   geom_point(position = position_dodge(width = 0.4)) +
#   geom_linerange(aes(ymin = ci_lower_predicted, ymax = ci_upper_predicted), position = position_dodge(width = 0.4)) +
#   coord_flip()

```

# Plots for publication

## Plot 1

Plot 1 shows the point estiamtes and bootstrapped 95% CIs for all participants, split by domain and measure.

```{r fig.height=4.5, fig.width=6}

ggsave(filename  = "plots/figure_1_cis_by_domain_iat_D.pdf",
       plot      = p_cis_by_domain,
       device    = "pdf",
       # path      = NULL,
       # dpi       = 300,
       units     = "in",
       width     = 6,
       height    = 4.5,
       limitsize = TRUE)

```

# Reviewer-requested Supplementary Analyses

Using the native scores of each measure.

```{r}

native_iat_scores <-   
read_rds("../../data/processed/data_processed_iat_D.rds")

native_amp_scores <-   
read_rds("../../data/processed/data_processed_amp_native.rds") |>
  mutate(measure = "amp")

native_gnat_scores <-   
read_rds("../../data/processed/data_processed_gnat_native.rds") |>
  mutate(measure = "gnat")

native_ept_scores <-   
read_rds("../../data/processed/data_processed_ept_native.rds") |>
  mutate(measure = "ept")


data_native_scores <- native_iat_scores |>
  bind_rows(native_amp_scores, native_gnat_scores, native_ept_scores) |>
  mutate(measure = case_match(measure,
                    "iat" ~ "IAT",
                    "biat" ~ "Brief IAT",
                    "siat" ~ "ST-IAT",
                    "amp" ~ "AMP",
                    "gnat" ~ "GNAT",
                    "ept" ~ "EPT"))


```

##RQ1. Proportion of scores differing from the zero point

###Caterpillar plot

```{r}

p_cis_by_domain_native_scores <-
  data_native_scores %>%
  arrange(estimate) %>%
  group_by(domain, measure) %>%
  mutate(ordered_id = row_number()/n()) %>%
  ungroup() %>%
  ggplot() +
  geom_linerange(aes(x = ordered_id, ymin = ci_lower, ymax = ci_upper, color = sig),
                 alpha = 1) +
  geom_point(aes(ordered_id, estimate), size = 0.5, shape = "square") +
  geom_hline(yintercept = 0, linetype = "dotted") +
  mdthemes::md_theme_linedraw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "top") +
  scale_color_viridis_d(end = 0.6, direction = -1) +
  xlab("Ranked participant") +
  ylab("PI score") +
  labs(color = "95% CI excludes zero point") +
  facet_grid(measure ~ domain, scales = "free")

p_cis_by_domain_native_scores

```

### Calculate scores

```{r}

data_diff_zero_native_scores <-
  data_native_scores %>%
  mutate(domain = as.factor(domain)) %>%
  group_by(domain, measure) %>%
  summarize(proportion_diff_zero = mean(sig, na.rm = TRUE),
            variance = var(sig, na.rm = TRUE),
            standard_error = plotrix::std.error(sig, na.rm = TRUE),
            .groups = "drop") %>%
  mutate(variance = ifelse(variance == 0, 0.001, variance))


```

### Meta

```{r}

# fit model
fit_diff_zero_native_scores <-
  lmer(proportion_diff_zero ~ 1 + measure + (1 | domain),
       weights = 1/variance,
       data = data_diff_zero_native_scores)

# extract re Tau
results_re_tau_diff_zero_native_scores <- fit_diff_zero_native_scores %>%
  merTools::REsdExtract() %>%
  as_tibble(rownames = "domain") %>%
  rename(tau = value)

# marginal means
results_diff_zero_native_scores <- fit_diff_zero_native_scores |>
  marginalmeans(variables = "measure") |>
  dplyr::select(measure = value, estimate, ci_lower = conf.low, ci_upper = conf.high) %>%
  mutate(se = ((ci_upper - ci_lower)/2) / 1.96,
         pi_lower = estimate - (1.96 * sqrt(se^2 + results_re_tau_diff_zero_native_scores$tau^2)),
         pi_upper = estimate + (1.96 * sqrt(se^2 + results_re_tau_diff_zero_native_scores$tau^2))) |>
  select(-se) 

# # plot
# p_nonzero_meta <-
#   ggplot(results_diff_zero, aes(fct_rev(measure), estimate)) +
#   #geom_linerange(aes(ymin = pi_lower, ymax = pi_upper), size = 0.5, linetype = "solid") +
#   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
#   geom_point(size = 2.5) +
#   mdthemes::md_theme_linedraw() +
#   scale_y_continuous(breaks = c(0, .25, .5, .75, 1), labels = c("0.00<br/>(Worse)", "0.25", "0.50", "0.75", "1.00<br/>(Better)")) +
#   labs(x = "",
#        y = "Proportion of participants<br/>with non-zero effects<br/>") +
#   theme(legend.position = "none") +
#   coord_flip(ylim = c(0, 1))
# 
# p_nonzero_meta

results_diff_zero_native_scores %>%
  round_df(2) %>%
  kable() %>%
  kable_classic(full_width = FALSE)

# tests
# using marginalmeans
fit_diff_zero_native_scores |>
  marginalmeans(variables = "measure", hypothesis = "pairwise") %>%
  mutate(p.value = ifelse(p.value < .001, "< .001", round_half_up(p.value, 3))) %>%
  round_df(2) %>%
  kable() %>%
  kable_classic(full_width = FALSE)

# using emmeans
# data_emms_diff_zero <- emmeans(fit_diff_zero, list(pairwise ~ measure), adjust = "holm")
# 
# summary(data_emms_diff_zero)$`pairwise differences of measure` %>%
#   as.data.frame() %>%
#   select(comparison = 1, p.value) %>%
#   mutate(p.value = ifelse(p.value < .001, "< .001", round_half_up(p.value, 3))) %>%
#   kable() %>%
#   kable_classic(full_width = FALSE)

```

### Combined plot

```{r}

data_diff_zero_combined_native_scores <-
  bind_rows(results_diff_zero_native_scores %>%
              mutate(domain = "Meta-analysis"),
            data_diff_zero_native_scores %>%
              mutate(ci_lower = proportion_diff_zero - standard_error*1.96,
                     ci_upper = proportion_diff_zero + standard_error*1.96) %>%
              select(measure, domain, estimate = proportion_diff_zero, ci_lower, ci_upper)) %>%
  mutate(domain = fct_relevel(domain, "Meta-analysis", "Self", "Race", "Politics"),
         point_size = case_when(domain == "Meta-analysis" ~ 2.5,
                                TRUE ~ 1.5))

p_nonzero_native_scores <-
  data_diff_zero_combined_native_scores %>%
  ggplot(aes(estimate, fct_rev(measure), color = domain, shape = domain)) +
  # geom_linerangeh(aes(xmin = pi_lower, 
  #                     xmax = pi_upper), 
  #                 size = 0.5, 
  #                 linetype = "dotted",
  #                 position = position_dodge(width = 0.6)) +
  geom_linerangeh(aes(xmin = ci_lower,
                      xmax = ci_upper),
                  position = position_dodge(width = 0.6)) +
  geom_point(aes(size = point_size), position = position_dodge(width = 0.6)) +
  scale_color_manual(values = c("#000000", viridisLite::viridis(begin = 0.4, end = 0.8, n = 3))) +
  scale_shape_manual(values = c(15, 16, 16, 16)) +
  scale_size(range = c(1.5, 2.5), guide = "none") +
  scale_x_continuous(breaks = c(0, .25, .5, .75, 1),
                     labels = c("0.00<br/>(Worse)", "0.25", "0.50", "0.75", "1.00<br/>(Better)"),
                     limits = c(0,1)) +
  #coord_flip(ylim = c(0, 1)) +
  mdthemes::md_theme_linedraw() +
  labs(x = "Proportion of participants<br/>with non-zero effects",
       y = "",
       color = "Domain",
       shape = "Domain") +
  theme(legend.position = "top",
        legend.title = element_blank()) +
  guides(color = guide_legend(reverse = TRUE),
         shape = guide_legend(reverse = TRUE))

p_nonzero_native_scores

```

## RQ2. Probability that differences can be detected between two participants' scores

### Calculate scores

```{r}

discriminability <- function(data, i) {
  data_with_indexes <- data[i,] # boot function requires data and index
  
  grid_estimates <- expand.grid(data_with_indexes$estimate, data_with_indexes$estimate) |>
    mutate(diff = Var1 - Var2,
           row_number = row_number(),
           modulus = row_number %% (nrow(data_with_indexes)+1)) |>
    filter(modulus != 1) |>
    select(diff)
  
  grid_se <- expand.grid(data_with_indexes$se, data_with_indexes$se) |>
    mutate(critical_value = 1.96 * sqrt(Var1^2 + Var2^2),
           row_number = row_number(),
           modulus = row_number %% (nrow(data_with_indexes)+1)) |>
    filter(modulus != 1) |>
    select(critical_value)
  
  proportion_sig_diff <-
    bind_cols(grid_estimates, grid_se) |>
    mutate(sig = abs(diff) > critical_value) |>
    summarize(proportion_sig_diff = mean(sig, na.rm = TRUE)) |>
    pull(proportion_sig_diff)
  
  return(proportion_sig_diff)
}

bootstrap_discriminability <- function(data){
  
  require(dplyr)
  require(boot)
  
  fit <-
    boot::boot(data      = data,
               statistic = discriminability,
               R         = 2000,
               sim       = "ordinary",
               stype     = "i",
               parallel  = "multicore",
               ncpus     = parallel::detectCores())
  
  results <- boot::boot.ci(fit, conf = 0.95, type = c("perc"))
  
  output <-
    tibble(
      estimate = fit$t0,
      ci_lower = results$percent[4],
      ci_upper = results$percent[5]
    )
  
  return(output)
}


# bootstrapping has a long execution time, so load saved values if they've already been calculated
if(file.exists("../../data/results/data_discriminability_native_scores.csv")) {
  
  data_discriminability_native_scores <- read_csv("../../data/results/data_discriminability_native_scores.csv") |>
    mutate(measure = fct_relevel(measure, "IAT", "Brief IAT", "ST-IAT", "AMP", "GNAT", "EPT"))
  
} else {
    
  # bootstrap D scores
  data_discriminability_native_scores <- data_native_scores |>
    mutate(se = (ci_upper - ci_lower)/(1.96*2)) |>
    select(session_id, domain, measure, estimate, se) |>
    mutate(measure = case_match(measure,
                                "iat" ~ "IAT",
                                "biat" ~ "Brief IAT", 
                                "siat" ~ "ST-IAT", 
                                "amp" ~ "AMP", 
                                "gnat" ~ "GNAT",
                                "ept" ~ "EPT")) |>
    group_by(domain, measure) |>
    do(bootstrap_discriminability(data = .)) |>
    ungroup() |>
    rename(proportion_discriminable = estimate) |>
    mutate(variance = ((ci_upper - ci_lower)/(1.96*2))^2,
           domain = as.factor(domain),
           measure = fct_relevel(measure, "IAT", "Brief IAT", "ST-IAT", "AMP", "GNAT", "EPT")) %>%
    mutate(variance = ifelse(variance == 0, 0.001, variance)) |>
    # model cannot be run on zero variance or 0 or 1, so offset by a minuscule amount
    mutate(
      proportion_discriminable_temp = case_when(proportion_discriminable < 0.001 ~ 0.001,
                                                proportion_discriminable > 0.999 ~ 0.999,
                                                TRUE ~ proportion_discriminable)
    ) %>%
    select(-proportion_discriminable_temp)
  
  # save to disk
  write_csv(data_discriminability_native_scores, "../../data/results/data_discriminability_native_scores.csv")
  
}

```

### Meta

```{r}

# fit meta analytic model
fit_disciminability_native_scores <-
  lmer(proportion_discriminable ~ 1 + measure + (1 | domain),
       weights = 1/variance,
       data = data_discriminability_native_scores)

# extract re Tau
results_re_tau_disciminability_native_scores <- fit_disciminability_native_scores %>%
  merTools::REsdExtract() %>%
  as_tibble(rownames = "measure") %>%
  rename(tau = value)

# extract marginal means
results_disciminability_native_scores <- fit_disciminability_native_scores |>
  marginalmeans(variables = "measure") |>
  dplyr::select(measure = value, estimate, ci_lower = conf.low, ci_upper = conf.high) %>%
  mutate(se = ((ci_upper - ci_lower)/2) / 1.96,
         pi_lower = estimate - (1.96 * sqrt(se^2 + results_re_tau_disciminability_native_scores$tau^2)),
         pi_upper = estimate + (1.96 * sqrt(se^2 + results_re_tau_disciminability_native_scores$tau^2))) |>
  select(-se) 

# # plot
# p_discriminability_meta <-
#   ggplot(results_disciminability, aes(fct_rev(measure), estimate)) +
#   #geom_linerange(aes(ymin = pi_lower, ymax = pi_upper), size = 0.5, linetype = "solid") +
#   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
#   geom_point(size = 2.5) +
#   scale_y_continuous(breaks = c(0, .25, .5, .75, 1), labels = c("0.00<br/>(Worse)", "0.25", "0.50", "0.75", "1.00<br/>(Better)")) +
#   scale_shape_manual(values = c(15, 16)) +
#   scale_color_viridis_d(begin = 0.3, end = 0.7) +
#   mdthemes::md_theme_linedraw() +
#   labs(x = "",
#        y = "Probability that differences can be detected<br/>between two participants' scores<br/>") +
#   theme(legend.position = "none") +
#   coord_flip(ylim = c(0, 1))
# 
# p_discriminability_meta

results_disciminability_native_scores %>%
  round_df(2) %>%
  kable() %>%
  kable_classic(full_width = FALSE)

# tests
fit_disciminability_native_scores |>
  marginalmeans(variables = "measure", hypothesis = "pairwise") %>%
  mutate(p.value = ifelse(p.value < .001, "< .001", round_half_up(p.value, 3))) %>%
  round_df(2) %>%
  kable() %>%
  kable_classic(full_width = FALSE)

```

### Combined plot

```{r}

data_disciminability_combined_native_scores <-
  bind_rows(results_disciminability_native_scores %>%
              mutate(domain = "Meta-analysis"),
            data_discriminability_native_scores %>%
              select(measure, domain, estimate = proportion_discriminable, ci_lower, ci_upper)) %>%
  mutate(domain = fct_relevel(domain, "Meta-analysis", "self", "race", "politics"),
         point_size = case_when(domain == "Meta-analysis" ~ 2.5,
                                TRUE ~ 1.5))

p_discriminability_native_scores <-
  data_disciminability_combined_native_scores %>%
  ggplot(aes(estimate, fct_rev(measure), color = domain, shape = domain)) +
  # geom_linerangeh(aes(xmin = pi_lower,
  #                     xmax = pi_upper),
  #                 size = 0.5,
  #                 linetype = "dotted",
  #                 position = position_dodge(width = 0.6)) +
  geom_linerangeh(aes(xmin = ci_lower,
                      xmax = ci_upper),
                  position = position_dodge(width = 0.6)) +
  geom_point(aes(size = point_size), position = position_dodge(width = 0.6)) +
  scale_color_manual(values = c("#000000", viridisLite::viridis(begin = 0.4, end = 0.8, n = 3))) +
  scale_shape_manual(values = c(15, 16, 16, 16)) +
  scale_size(range = c(1.5, 2.5), guide = "none") +
  scale_x_continuous(breaks = c(0, .25, .5, .75, 1),
                     labels = c("0.00<br/>(Worse)", "0.25", "0.50", "0.75", "1.00<br/>(Better)")) +
  coord_cartesian(xlim = c(0, 1)) +
  mdthemes::md_theme_linedraw() +
  labs(x = "Probability that differences can be detected<br/>between two participants' scores<br/>",
       y = "",
       color = "Domain",
       shape = "Domain") +
  # theme(legend.position = "top",
  #       legend.title = element_blank()) +
  theme(legend.position="none") +
  guides(color = guide_legend(reverse = TRUE),
         shape = guide_legend(reverse = TRUE))

p_discriminability_native_scores

```

## RQ3. Proportion of observed range of 95% CI widths covered by individual participants' 95% CIs

NB observed range of confidence intervals

### Calculate scores

```{r}

## calculate observed ranges
observed_range_estimates_native_scores <- data_native_scores %>%
  group_by(measure, domain) %>%
  dplyr::summarize(min = min(ci_lower, na.rm = TRUE),
                   max = max(ci_upper, na.rm = TRUE),
                   .groups = "drop") %>%
  mutate(range = max - min)

# calculate CI / range
data_ci_width_proportions_native_scores <- data_native_scores %>%
  # join this data into the original data
  full_join(observed_range_estimates_native_scores, by = c("measure", "domain")) %>%
  # calculate ci width as a proportion of observed range
  mutate(ci_width_proportion = ci_width / range,
         domain = as.factor(domain),
         measure = fct_relevel(measure, "IAT", "Brief IAT", "ST-IAT", "AMP", "GNAT", "EPT")) %>%
  group_by(domain, measure) %>%
  summarize(ci_width_proportion_mean = mean(ci_width_proportion, na.rm = TRUE),
            variance = plotrix::std.error(ci_width_proportion)^2) %>%
  ungroup() 

```

### Meta

```{r}

# fit model
fit_ci_width_proportions_native_scores <-
  lmer(ci_width_proportion_mean ~ 1 + measure + (1 | domain),
       weights = 1/variance,
       data = data_ci_width_proportions_native_scores)

# extract re Tau
results_re_tau_ci_width_proportions_native_scores <- fit_ci_width_proportions_native_scores %>%
  merTools::REsdExtract() %>%
  as_tibble(rownames = "measure") %>%
  rename(tau = value)

# extract marginal means
results_ci_width_proportions_native_scores <- 
  fit_ci_width_proportions_native_scores |>
  marginalmeans(variables = "measure") |>
  dplyr::select(measure = value, estimate, ci_lower = conf.low, ci_upper = conf.high) %>%
  mutate(se = ((ci_upper - ci_lower)/2) / 1.96,
         pi_lower = estimate - (1.96 * sqrt(se^2 + results_re_tau_ci_width_proportions_native_scores$tau^2)),
         pi_upper = estimate + (1.96 * sqrt(se^2 + results_re_tau_ci_width_proportions_native_scores$tau^2))) |>
  select(-se) 

# # plot
# p_coverage_meta <-
#   ggplot(results_ci_width_proportions, aes(fct_rev(measure), estimate)) +
#   #geom_linerange(aes(ymin = pi_lower, ymax = pi_upper), size = 0.5, linetype = "solid") +
#   geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
#   geom_point(size = 2.5) +
#   mdthemes::md_theme_linedraw() +
#   scale_y_continuous(breaks = c(0, .25, .5, .75, 1), labels = c("0.00<br/>(Better)", "0.25", "0.50", "0.75", "1.00<br/>(Worse)")) +
#   labs(x = "",
#        y = "Proportion of observed range covered <br/>by individual participants' 95% CIs") +
#   theme(legend.position = "none") +
#   coord_flip(ylim = c(0, 1))
# 
# p_coverage_meta

results_ci_width_proportions_native_scores %>%
  round_df(2) %>%
  kable() %>%
  kable_classic(full_width = FALSE)

# tests
fit_ci_width_proportions_native_scores |>
  marginalmeans(variables = "measure", hypothesis = "pairwise") %>%
  mutate(p.value = ifelse(p.value < .001, "< .001", round_half_up(p.value, 3))) %>%
  round_df(2) %>%
  kable() %>%
  kable_classic(full_width = FALSE)

```

### Combined plot

```{r}

data_coverage_combined_native_scores <-
  bind_rows(results_ci_width_proportions_native_scores %>%
              mutate(domain = "Meta-analysis"),
            data_ci_width_proportions_native_scores %>%
              mutate(ci_lower = ci_width_proportion_mean - sqrt(variance)*1.96,
                     ci_upper = ci_width_proportion_mean + sqrt(variance)*1.96) %>%
              select(measure, domain, estimate = ci_width_proportion_mean, ci_lower, ci_upper)) %>%
  mutate(domain = fct_relevel(domain, "Meta-analysis", "self", "race", "politics"),
         point_size = case_when(domain == "Meta-analysis" ~ 2.5,
                                TRUE ~ 1.5))

p_coverage_native_scores <-
  data_coverage_combined_native_scores %>%
  ggplot(aes(estimate, fct_rev(measure), color = domain, shape = domain)) +
  # geom_linerangeh(aes(xmin = pi_lower,
  #                     xmax = pi_upper),
  #                 size = 0.5,
  #                 linetype = "dotted",
  #                 position = position_dodge(width = 0.6)) +
  geom_linerangeh(aes(xmin = ci_lower,
                      xmax = ci_upper),
                  position = position_dodge(width = 0.6)) +
  geom_point(aes(size = point_size), position = position_dodge(width = 0.6)) +
  scale_color_manual(values = c("#000000", viridisLite::viridis(begin = 0.4, end = 0.8, n = 3))) +
  scale_shape_manual(values = c(15, 16, 16, 16)) +
  scale_size(range = c(1.5, 2.5), guide = "none") +
  scale_x_continuous(breaks = c(0, .25, .5, .75, 1),
                     labels = c("0.00<br/>(Better)", "0.25", "0.50", "0.75", "1.00<br/>(Worse)"),
                     limits = c(0,1)) +
  mdthemes::md_theme_linedraw() +
  labs(x = "Proportion of observed range covered <br/>by individual participants' 95% CIs",
       y = "",
       color = "Domain",
       shape = "Domain") +
  # theme(legend.position = "top",
  #       legend.title = element_blank()) +
  theme(legend.position="none") +
  guides(color = guide_legend(reverse = TRUE),
         shape = guide_legend(reverse = TRUE))

p_coverage_native_scores

```

## Plots for the supplement

### Plot 1

Plot 1 shows the point estiamtes and bootstrapped 95% CIs for all participants, split by domain and measure, for the native scores.

```{r fig.height=7, fig.width=6}

p_cis_by_domain_native_scores

ggsave(filename  = "plots/figure_s1_cis_by_domain.pdf",
       plot      = p_cis_by_domain_native_scores,
       device    = cairo_pdf,
       # path      = NULL,
       # dpi       = 300,
       units     = "in",
       width     = 6,
       height    = 7,
       limitsize = TRUE)

```

### Plot 2

```{r fig.height=12, fig.width=6}

p_combined_native_scores <-
  p_nonzero_native_scores +
  p_discriminability_native_scores +
  p_coverage_native_scores +
  plot_layout(ncol = 1)

p_combined_native_scores

ggsave(filename  = "plots/figure_s2_metaanalyses.pdf",
       plot      = p_combined_native_scores,
       device    = cairo_pdf,
       # path      = NULL,
       # dpi       = 300,
       units     = "in",
       width     = 6,
       height    = 12,
       limitsize = TRUE)

```



# Session info

```{r}

sessionInfo()

```
