---
title: "Comparing 6 implicit measures' suitability for individual use"
author: "Jamie Cummins & Ian Hussey"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}
knitr::opts_chunk$set(message=FALSE,
                      warning=FALSE,
                      cache.lazy=FALSE)
```

```{r}

# dependencies
library(tidyverse)
library(knitr)
library(kableExtra)
library(boot)
library(parallel)
library(bayestestR)
library(patchwork)
library(mdthemes)
library(lme4)
library(sjPlot)
library(marginaleffects)
library(ggstance)
library(janitor)
# library(merTools) called via merTools:: to avoid namespace collisions between MASS and dplyr

# create necessary directories
dir.create("../../data/results")
dir.create("plots")

# set seed for reproducibility
set.seed(42)

# options
options(knitr.table.format = "html") # necessary configuration of tables

# disable scientific notation
options(scipen = 999)


# function to round all numeric vars in a data frame
round_df <- function(df, n_digits = 3) {
  require(janitor)
  df %>% mutate_if(is.numeric, janitor::round_half_up, digits = n_digits)
}

```

# Load in explicit data

```{r}

data_explicit_measures <- read_rds("../../data/processed/explicit_vars/data_processed.rds")

```

# MAP precision of each of the three measures

## MAP CI width

```{r}

data_map_explicit_ci_widths <- data_explicit_measures %>%
  group_by(scale) %>%
  do(point_estimate(.$ci_width, centrality = "MAP")) %>%
  ungroup()

data_map_explicit_ci_widths %>%
  pivot_wider(names_from = scale, values_from = MAP) %>%
  round_df(2) %>%
  t() %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)


```

## plot

```{r}

p_cis_by_domain_explicit <-
  data_explicit_measures %>%
  arrange(estimate) %>%
  group_by(scale) %>%
  mutate(ordered_id = row_number()/n()) %>%
  ungroup() %>%
  ggplot() +
  geom_linerange(aes(x = ordered_id, ymin = ci_lower, ymax = ci_upper),
                 alpha = 1) +
  geom_point(aes(ordered_id, estimate), size = 0.5, shape = "square") +
  mdthemes::md_theme_linedraw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "top") +
  scale_color_viridis_d(end = 0.6, direction = -1) +
  xlab("Ranked participant") +
  ylab("Scale score") +
  facet_grid(~scale)

p_cis_by_domain_explicit

```


# Discriminability between participants

There is no zero point in the scales, so estimating difference from it would not be possible. So we move straight to discriminability between participants. 

```{r}

# function for discriminability assessment
discriminability <- function(data, i) {
  data_with_indexes <- data[i,] # boot function requires data and index
  
  grid_estimates <- expand.grid(data_with_indexes$estimate, data_with_indexes$estimate) |>
    mutate(diff = Var1 - Var2,
           row_number = row_number(),
           modulus = row_number %% (nrow(data_with_indexes)+1)) |>
    filter(modulus != 1) |>
    select(diff)
  
  grid_se <- expand.grid(data_with_indexes$se, data_with_indexes$se) |>
    mutate(critical_value = 1.96 * sqrt(Var1^2 + Var2^2),
           row_number = row_number(),
           modulus = row_number %% (nrow(data_with_indexes)+1)) |>
    filter(modulus != 1) |>
    select(critical_value)
  
  proportion_sig_diff <-
    bind_cols(grid_estimates, grid_se) |>
    mutate(sig = abs(diff) > critical_value) |>
    summarize(proportion_sig_diff = mean(sig, na.rm = TRUE)) |>
    pull(proportion_sig_diff)
  
  return(proportion_sig_diff)
}

# function for bootstrapping discriminability assessment 
bootstrap_discriminability <- function(data){
  
  require(dplyr)
  require(boot)
  
  fit <-
    boot::boot(data      = data,
               statistic = discriminability,
               R         = 2000,
               sim       = "ordinary",
               stype     = "i",
               parallel  = "multicore",
               ncpus     = parallel::detectCores())
  
  results <- boot::boot.ci(fit, conf = 0.95, type = c("perc"))
  
  output <-
    tibble(
      estimate = fit$t0,
      ci_lower = results$percent[4],
      ci_upper = results$percent[5]
    )
  
  return(output)
}

# bootstrapping has a long execution time, so load saved values if they've already been calculated
if(file.exists("../../data/results/explicit_vars/data_explicit_discriminability.csv")) {
  
  data_discriminability <- read_csv(
    "../../data/results/explicit_vars/data_explicit_discriminability.csv"
    ) |>
    mutate(scale = fct_relevel(scale, "rse", "rwa", "mrs"))
  
} else {
  
  # bootstrap D scores
  data_discriminability <- data_explicit_measures |>
    mutate(se = (ci_upper - ci_lower)/(1.96*2)) |>
    select(session_id, scale, estimate, se) |>
    group_by(scale) |>
    do(bootstrap_discriminability(data = .)) |>
    ungroup() |>
    rename(proportion_discriminable = estimate) |>
    mutate(variance = ((ci_upper - ci_lower)/(1.96*2))^2,
           scale = fct_relevel(scale, "rse", "rwa", "mrs")) %>%
    mutate(variance = ifelse(variance == 0, 0.001, variance)) |>
    # model cannot be run on zero variance or 0 or 1, so offset by a minuscule amount
    mutate(
      proportion_discriminable_temp = case_when(proportion_discriminable < 0.001 ~ 0.001,
                                                proportion_discriminable > 0.999 ~ 0.999,
                                                TRUE ~ proportion_discriminable)
    ) %>%
    select(-proportion_discriminable_temp)
  
  # save to disk
  write_csv(data_discriminability,
            "../../data/results/explicit_vars/data_explicit_discriminability.csv")
  
}

```

## Discriminability estimates

```{r}

data_discriminability

```


# Coverage of scores

## Calculate scores

```{r}

## calculate observed ranges
observed_range_estimates_explicit <- data_explicit_measures %>%
  group_by(scale) %>%
  dplyr::summarize(min = min(ci_lower, na.rm = TRUE),
                   max = max(ci_upper, na.rm = TRUE),
                   .groups = "drop") %>%
  mutate(range = max - min)

# calculate CI / range
data_ci_width_proportions_explicit <- data_explicit_measures %>%
  # join this data into the original data
  full_join(observed_range_estimates_explicit, by = c("scale")) %>%
  # calculate ci width as a proportion of observed range
  mutate(ci_width_proportion = ci_width / range,
         scale = fct_relevel(scale, "rse", "rwa", "mrs")) %>%
  group_by(scale) %>%
  summarize(ci_width_proportion_mean = mean(ci_width_proportion, na.rm = TRUE),
            variance = plotrix::std.error(ci_width_proportion)^2) %>%
  ungroup() 

```

## FE-Model

```{r}

# fit model
fit_ci_width_proportions <-
  data_explicit_measures |>
       mutate(scale = as.factor(scale),
              ci_width_proportion = case_when(
                scale == "mrs" ~ 
                  ci_width / (observed_range_estimates_explicit |> filter(scale == "mrs") |> pull(range)),
                scale == "rse" ~ 
                  ci_width / (observed_range_estimates_explicit |> filter(scale == "rse") |> pull(range)),
                scale == "rwa" ~ 
                  ci_width / (observed_range_estimates_explicit |> filter(scale == "rwa") |> pull(range))
              )) |>
  ungroup() %>%
  lm(ci_width_proportion ~ scale,
       data = .) 

predictions(fit_ci_width_proportions,
            by = "scale",
            newdata = datagrid(grid_type = "balanced"))

# extract marginal means
results_ci_width_proportions <- fit_ci_width_proportions |>
  predictions(variables = "scale") |>
  dplyr::select(scale, estimate, ci_lower = conf.low, ci_upper = conf.high) 

```


# Session info

```{r}

sessionInfo()

```
